---
title: "Reproduction of Faber 2012"
output: html_notebook
---

###So whats changed since 2012? 

Loading data until 2016

```{r}
require(quantstrat)

#Import saved pricing data csv files as xts
rm(list = ls())

symbols <- c("SP500","EAFE","US10YR","GSCI","NAREIT")

getSymbols(symbols,
           src = "csv",
           dir="FinalData",
           col.names=c("Close"))

```

To do:

- make output quiet

#### Manipulating the data

```{r}
AllAssets <- cbind.xts(Cl(SP500),
                       Cl(EAFE),
                       Cl(US10YR),
                       Cl(GSCI),
                       Cl(NAREIT))                       

AllAssets <- AllAssets["1972-12-31::2016-12-31"]
colnames(AllAssets) <- symbols

AllAssets.ret <- Return.calculate(AllAssets)[-1,]
AllAssets.cumret <- 100*cumprod(1+ ROC(AllAssets, type = "discrete")[-1,])

chart.TimeSeries(AllAssets.cumret,
                 main = "Figure 3 - Asset Class Returns 1973-2016, Log Scale",
                 #lty = "2",
                 ylab = "",
                 ylog = TRUE,
                 ylim = c(40,6000),
                 date.format = "%Y",
                 major.ticks = "years",
                 legend.loc = "bottomright",
                 colorset = 1:12, #bluefocus, #create own colorset at some point
                 minor.ticks =FALSE)

chart.TimeSeries(AllAssets.cumret["2012::2016"],
                 main = "Figure 3 - Asset Class Returns 1973-2012, Log Scale",
                 #lty = "2",
                 ylab = "",
                 ylog = FALSE,
                 #ylim = c(40,6000),
                 date.format = "%Y",
                 major.ticks = "years",
                 legend.loc = "topleft",
                 colorset = 1:12, #bluefocus, #create own colorset at some point
                 minor.ticks =FALSE)

```

Whats changed:

- Commodities have had negative returns


####Analysing returns and drawdowns.

```{r}
Originalreturns <- table.AnnualizedReturns(AllAssets.ret["1972-12-31::2012-12-31"], 
                        scale = 12, 
                        Rf = ((1+0.0541)^(1/12))-1, #not same as 5.41%?
                        geometric = TRUE, 
                        digits = 4)
Extendedreturns <- table.AnnualizedReturns(AllAssets.ret["1972-12-31::2016-12-31"], 
                        scale = 12, 
                        Rf = ((1+0.0541)^(1/12))-1, #not same as 5.41%?
                        geometric = TRUE, 
                        digits = 4)

Originalreturns
Extendedreturns

Change <- Extendedreturns - Originalreturns
Change
```

Changes:

- S&P500 has improved returns, lower std dev and a better sharp ratio
- EAFE0 has lower returns, lower std dev amd a worse sharp ratio
- US10YR has lower returns, lower stdev and a much worse sharp ratio
- GSCI has much lower returns for much the same volatility resulting in a much worse sharp ratio thats close to 0
- NAREIT is relatively unchanged - slightly lower stdev gives it a slight better sharpe ratio

```{r}
MaxDD <- rbind(round(maxDrawdown(AllAssets.ret["1972-12-31::2012-12-31"], weights = NULL, geometric = TRUE, invert = FALSE),4),
      round(maxDrawdown(AllAssets.ret["1972-12-31::2016-12-31"], weights = NULL, geometric = TRUE, invert = FALSE),4))
rownames(MaxDD) <- c("1973-2012","1973-2016")
print(MaxDD)
```
Changes:

- GSCI in a much larger drawdown (81%)

####Drawdown chart

```{r}
chart.Drawdown(AllAssets.ret$`GSCI`["1972-12-31::2016-12-31"],
               main = "GSCI Drawdowns 1973-2016",
               ylab = "",
               date.format = "%Y",
               major.ticks = "years",
               colorset = redfocus)

```

####Managing Risk 

Faber introduces a timing system for investors to use to manage the risk.... using a 10 month simple moving average timing model

```{r}
myChart_Theme <- chart_theme() #Create a chart_theme
myChart_Theme$col$line.col <- "blue"

SMAperiod <- 10

chart_Series(Cl(GSCI),
             name = "GSCI vs 10 Month Simple Moving Average",
             theme=myChart_Theme,
             type = "line",
             subset = "1990-12-31::2016-12-31",
             TA = 'add_SMA(n=SMAperiod, on=1, col="red")'
             )
```

Thoughts:

- GSCI no longer a diversifying asset?
- Or has timing signal removed exposure to it in 2014, saving the strategy from most of the drawdown and still should be included.

