---
title: "Return calcs - S&P"
output: html_notebook
---

```{r, include=FALSE}
#clear workspace
rm(list = ls())

#load packages
library(tidyverse)
require(quantstrat)
```

```{r, include=FALSE}
#import pricing
symbols <- c("SP500","TBills") #,"EAFE","US10YR","GSCI","NAREIT")

getSymbols(symbols,
           src = "csv",
           dir="FinalData",
           col.names=c("Close"))
```

```{r}
AllAssets <- cbind.xts(Cl(SP500),
                       Cl(TBILLS))#,Cl(US10YR), Cl(GSCI),Cl(NAREIT))    

#create dataframe - tidyverse not compatible with xts?
AllAssets.df <- data.frame(date=index(AllAssets), coredata(AllAssets)) #, row.names = index(AllAssets))

```


```{r}
#mutate new columns
AllAssets.df  <- mutate(AllAssets.df, 
  "10mSMA" = rollmean(SP500.Close,10,fill = 0,align = "right"),
  "Asset.ret" = c(0,diff(SP500.Close)/lag(SP500.Close)[-1]),
  "Rf.ret" = lag((TBILLS.Close/100)/12),
  "signal" = lag(ifelse(SP500.Close>`10mSMA`,1,0)),
  "Timing.ret" = ifelse(signal == 1,Asset.ret,Rf.ret) 
)

rownames(AllAssets.df) <- index(AllAssets)
```

####To do:

* check lag correct
* run over 1900 data / other assets

####Convert back to xts to be able to subset?

```{r}
AllAssets <- as.xts(AllAssets.df[,-1])
```

```{r}
Returns <- cbind.xts(AllAssets$Asset.ret, AllAssets$Timing.ret)["1972-12-31::2012-12-31"]
```

####Stats

```{r}
stats <- rbind(Return.annualized(Returns,scale = 12)*100, 
               StdDev.annualized(Returns,scale = 12)*100, 
               SharpeRatio.annualized(Returns,Rf = 0.0541/12),
               maxDrawdown(Returns,scale = 12)*100,
               c(nrow(subset(Returns, Returns$Asset.ret >= 0))/nrow(Returns),nrow(subset(Returns, Returns$Timing.ret >= 0))/nrow(Returns)))

colnames(stats) <- c("S&P 500", "Timing")
rownames(stats) <- c("Returns","Volatility","Sharpe","MaxDD","% Positive Months")#,"$100 becomes","Inflation CAGR")
stats
```

#### to do:

* round / format with % symbol

####Charts 

```{r}
charts.PerformanceSummary(Returns,
                          main = "S&P 500 Total Returns vs Timing Total Returns (1973-2012)",
                          date.format = "%Y",
                          colorset = c(4,2),
                          ylog = FALSE,
                          minor.ticks =FALSE)
```

```{r}
charts.RollingPerformance(Returns,
                          width = 12,
                          main = "S&P 500 12M Rolling Total Returns vs Timing 12M Rolling  Total Returns (1973-2012)",
                          date.format = "%Y",
                          colorset = c(4,2),
                          ylog = FALSE,
                          minor.ticks =FALSE)
```

to do

* make it easy to see difference, explore different widths/periods, add legend

####To do:

* format charts - e.g. log chart, start at 100, colours
* get data back to 1900
* create % positive months, $100 becomes, inflation CAGR etc
* Get ten worst years
* rolling returns / alpha


